Exploring the Design Space of Differentially Private Bayesian Inference under Hellinger Distance

### 2019-01-16 ICML2019/main.tex
starting a pass on the abstract

\begin{abstract}
% Several approaches have been explored in order to make Bayesian inference
% differentially private.
% For instance, \cite{dimitrakakis2014robust} and
% \cite{wang2015privacy} proved that, under specific conditions of the likelihood function and the prior distribution,
% sampling from the posterior distribution, is already differentially private. \cite{zhang2016differential} and \cite{foulds2016theory}
% designed differentially private (d.p.) mechanisms by adding laplacian noise
% to the numeric parameters of the posterior distributions. 
% Accuracy, is usally (\cite{??}) measured by providing upper bounds, holding w.h.p, on the
% $\ell_1$ or $\ell_\infty$-distance between the numeric parameters
% of the released posterior distribution and the actual real ones of posterior distribution.
We explore the design space of differentially private Bayesian
inference mechanisms with accuracy measured in terms of Hellinger
distance over posterior distributions.  
We focus on two discrete models for parametric Bayesian
inference: the Beta-Binomial and the Dirichlet-Multinomial
models. We study two mechanisms based on the 
Laplace perturbation of the parameters of the posterior distribution under
$\ell_1$ norm, and compare them with variations of the Exponential
mechanism where the score function is based on the Hellinger distance.
Accuracy is measured through the Hellinger distance between the posterior
distribution released by the different mechanisms and the real one.
We compare the accuracy theoretically and experimentally.
\end{abstract}
 % TODO: replace with your keywords

\section{Introduction}
\label{sec_intro}
Data analysis techniques are broadly used in various applications in different areas to improve their services, including disease-medicine service, financial service, location service, social network and so on. In order to provide a better service, large of data are collected from users for analysis. As a consequence, the data privacy came to be a critical issue. Sensitivity information in data can be revealed through the analysis results. The key challenge here is to release a private analysis results, from which adversary cannot observe individual's sensitive information in data.

Plenty of work have been developed to solve this issue, guaranteeing the privacy in specific data analysis algorithms. They achieved the $\epsilon-$differential privacy by adopting either Laplace mechanism or achieved the $(\epsilon, \delta)-$differential privacy. But they are not giving better accuracy than the differential privacy mechanism itself. Here, we are proposing mechanism with better accuracy.

>>>>

\begin{abstract}
% Several approaches have been explored in order to make Bayesian inference
% differentially private.
% For instance, \cite{dimitrakakis2014robust} and
% \cite{wang2015privacy} proved that, under specific conditions of the likelihood function and the prior distribution,
% sampling from the posterior distribution, is already differentially private. \cite{zhang2016differential} and \cite{foulds2016theory}
% designed differentially private (d.p.) mechanisms by adding laplacian noise
% to the numeric parameters of the posterior distributions. 
% Accuracy, is usally (\cite{??}) measured by providing upper bounds, holding w.h.p, on the
% $\ell_1$ or $\ell_\infty$-distance between the numeric parameters
% of the released posterior distribution and the actual real ones of posterior distribution.
We explore the design space of differentially private Bayesian
inference mechanisms with accuracy measured in terms of Hellinger
distance over posterior distributions.  
We focus on two discrete models for parametric Bayesian
inference: the Beta-Binomial and the Dirichlet-Multinomial
models. We study two mechanisms based on the 
Laplace perturbation of the parameters of the posterior distribution under
$\ell_1$ norm, and compare them with a discrete mechanism calibrating 
its score function to a smooth bound on the Hellinger distance.
Accuracy is measured through the Hellinger distance between the posterior
distribution released by the different mechanisms and the real one.
We compare the accuracy theoretically and experimentally.
\end{abstract}
 % TODO: replace with your keywords

\section{Introduction}
\label{sec_intro}
Data analysis techniques have brought significant improvements in a
variety of applications including applications from the medical,
financial, social, and transportation fields. In order to provide
better services, these applications need large amounts of users data
putting at risk the privacy of individual users contributing their data. 
Differential privacy was proposed a decade ago to address these
situations and it on its way to become a gold standard in data
privacy.

Bayesian inference is a standard statistical tool that is useful to
estimate a posterior distribution when given a prior distribution and
some observed data.

In this work we consider the design space of  parametric Bayesian
inference mechanisms guaranteeing differential privacy. Our work is
motivated by recent developments in the area of probabilistic
programming where several tools have been proposed to perfor
parametric and non-parametric Bayesian inference in an efficient
way. The in
for our work is the recent development of

In particular
we focus on two classical models: the Beta-Binomial and the
Dirichlet-Multinomial models. These are classical models
